---
title: "TD2: Étude de données"
author: ""
date: "25 septembre 2015"
output: html_document
---


```{r echo=FALSE}
county = read.csv("Data/county_facts.csv")
votes = read.csv("Data/votes.csv")
library(ggplot2)
library(grid)
library("gridExtra")
library(ggplot2)
library(lattice)
```
We work on the amrican election. We have that set of data:
```{r}
library(ggplot2)
interest<-subset(votes,select=c('White','Trump','Romney','Clinton','Obama','Edu_batchelors'))
head(interest)
```
With each line corresponding to an american county.
Getting usefull result is hard because we work on percentage. To get correlation on for instance white votes, we have to work on counties were there is almost only whites. We saw on that website : http://tempsreel.nouvelobs.com/monde/20161109.OBS0936/les-5-facteurs-cles-qui-expliquent-la-victoire-de-donald-trump.html that white republicans shouldn't vote for trump relating to there university education. So we select only white counties (over 95%) and we plot the difference between the two previous votes for republicans and democrates. That show that the number of white republicans voters grows counter to white democrate vote.
```{r}

interest=interest[interest$White>0.95, ]
interest$diffTR = interest$Trump-interest$Romney
interest$diffCO = interest$Clinton-interest$Obama
p1=ggplot(data=interest,aes(x=White, y=diffTR))+geom_point(alpha=0.1)+stat_summary(fun.y = "median", colour = "red", size = 2, geom = "point")+ggtitle("White counties republican vote evolution")
p2=ggplot(data=interest,aes(x=White, y=diffCO))+geom_point(alpha=0.1)+stat_summary(fun.y = "median", colour = "red", size = 2, geom = "point")+ggtitle("White counties democrate vote evolution")
grid.arrange(p1, p2, ncol=2)
```
After we can look at the impact of education:  
```{r}
p1<-ggplot(data=interest,aes(x=Edu_batchelors, y=diffTR))+geom_point(alpha=0.1)+ggtitle("White counties democrate vote evolution regarding education")
p2<-ggplot(data=interest,aes(x=Edu_batchelors, y=diffCO))+geom_point(alpha=0.1)+ggtitle("White counties democrate vote evolution regarding education")
grid.arrange(p1, p2, ncol=2)
```

